SunPy - Python for Solar Physics

### 2014-01-28 authors.tex
Add new author list

\author{The SunPy Community}
\address{\url{http://sunpy.org}}
\ead{sunpy@googlegroups.com}

\author{Stuart J Mumford}
\address{Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), School of 
Mathematics and Statistics, The University of Sheffield, Hicks Building, 
Hounsfield Road, Sheffield, S3 7RH U.K.}

\author{Steven Christe}\
\address{NASA Goddard Space Flight Center, Greenbelt, U.S.A.}

\author{David P\'erez-Su\'arez}
\address{South African National Space Agency - Space Science,
Hospital Street, 7200 Hermanus, Western Cape, South Africa}

\author{Andrew R Inglis}
\address{NASA Goddard Space Flight Center, Greenbelt, USA}
\address{The Catholic University of America, Washington, DC, USA}

\author{Jack Ireland}
\address{ADNET Systems Inc., Mail Code 671.1, NASA Goddard Space
  Flight Center, Greenbelt, MD, U.S.A.}

\author{Albert Y. Shih}
\address{NASA Goddard Space Flight Center, Greenbelt, MD, USA}

\author{}
\address{}

>>>>

\author{The SunPy Community,}
\address{\url{http://sunpy.org}}
\ead{sunpy@googlegroups.com}

\author{
% People who have directly contributed to the text, still in no order.
Stuart J Mumford$^1$,
Steven Christe$^2$,
David P\'erez-Su\'arez$^3$,
Andrew R Inglis$^{2,5}$,
Jack Ireland$^{6,2}$,
Albert Y Shih$^2$,
% Contributors to SunPy Sorted thus:
% No. Commits to main repo + commits in open PR's
% Date of most recent contribution
F Mayer, %721
K Hughitt, %446
R Hewett, %88
Nabil Freij$^1$, %52
M Earnshaw, %52
T Meszaros, %17
N Chorley, %17
Samuel M Bennett$^1$, %14
M Malocha, %10
J Evans, %10
A Maverick, %8
M Bates, %6
Andrew J Leonard$^7$, %3
J Ballew, %3
T Robitaille, %2
B Mampaey, %2
%Hypnus1803 %1
and 
A Kustov %1
}

\address{
$^1$ Solar Physics \& Space Plasma Research Centre (SP$^{2}$RC), 
School of Mathematics and Statistics, The University of Sheffield, Hicks 
Building, Hounsfield Road, Sheffield, S3 7RH U.K.,

$^2$NASA Goddard Space Flight Center, Greenbelt, MD, USA,

$^3$South African National Space Agency - Space Science, Hospital 
Street, 7200 Hermanus, Western Cape, South Africa,

$^5$ The Catholic University of America, Washington, DC, USA,

$^6$ADNET Systems Inc., Mail Code 671.1,

$^7$Department of Mathematics and Physics, Aberystwyth University, 
Physical Sciences Building, Aberystwyth, Ceredigion, SY23 3BZ,
}
